### 2020-05-30 paper/paper.tex
First commit

\documentclass[conference]{IEEEtran}
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{physics}
\begin{document}

\title{Factoring RSA keys with Shor's algorithm}

\author{\IEEEauthorblockN{Giulio Muscarello}}

\maketitle

\begin{abstract}
RSA is a well-known public cryptography scheme that relies on the integer factorization problem. Shor's algorithm, first described in 1994, factorizes integers in polynomial time using a quantum computer. We present an improvement to the Qiskit implementation of Shor's algorithm and demonstrate an attack on communications protected by RSA.
\end{abstract}

\section{Introduction}
We know from the fundamental theorem of arithmetic that every positive integer has a unique prime factorization. There are no known classical algorithms that can factor integers in polynomial time; in fact, the problem of whether such an algorithm exists is known as the "integer factorization problem". Many cryptographic schemes are based on the difficulty of factoring composite integers. Among them, RSA is the most common cryptosystem.

Shor proved \cite{shor} that quantum computers can solve the factorization problem in linear time, and developed an algorithm for this purpose. The impact of quantum computers on the security of encrypted data and communications is therefore a key concern in the security community, and the development of so-called "post-quantum cryptography" is an active area of research. This paper presents a demonstration of Shor's algorithm to attack a toy RSA example.

\section{Algorithms}
\subsection{RSA}
RSA is an asymmetric cryptosystem, meaning that it produces a "public key" and a "private key". Any person can thus encrypt a message using the receiver's public key, and the receiver can decrypt it with his private key. Today RSA sees wide implementation, securing all sorts of communications from Internet browsing to e-mail traffic to instant messaging.

A mathematical description of RSA is out of scope for this paper, and can be found in \cite{rsa}. For the purposes of this paper, the cryptosystem can be thought of as a private key $A = \{p, q\}$, where $p$ and $q$ are primes known only to the receiver, and a public key $n=pq$, which can be disseminated. The public key allows any third party to encrypt messages, and the private key allows the receiver to decrypt messages intended for him.

\subsection{Reduction to the order-finding problem}
Miller \cite{miller} proved that the problem of factoring $N$ can be reduced to the "period-finding problem": for a given $a < N - 1$, find the smallest $r$ such that $a^r \equiv 1 \mod N$ (i.e. find the order of the algebraic group of integers coprime with $N$ and smaller than $N$, hence the name of "order-finding problem" by which it is found in literature). Specifically, depending on the choice of $a$ we have that either:
\begin{itemize}
\item $N$ and $a$ have some common prime factors, in which case $p=\gcd(N, a)$ returns one prime and $N/p$ returns the other;
\item let $r$ be the period defined above, then at least one of $p, q = \gcd(N, a^{r/2}\pm 1)$ are factors of $N$;
\item neither hold, we had a "bad" choice of $a$.
\end{itemize}

It can be shown that in the generic case where $N$ has $k$ prime factors, the algorithm above yields a factor with probability $p=1-2^{1-k}$; in the case of RSA, $p=0.5$.

The random choice of $a$ and the computation of possible factors is known as the "classical part" of Shor's algorithm. The solution to the period-finding problem however is of greater theoretical interest, and can be solved by the quantum algorithm that is at the core of Shor's algorithm.

\subsection{Order-finding subroutine}
We can further reduce the order-finding problem to the well-known problem of finding the eigenvalues of a unitary operator, which can be solved with the quantum phase estimation algorithm. Shor exploits the unitary operator
\begin{equation}
U_a: x \rightarrow ax \mod N
\end{equation}
whose eigenvalues\footnote{The reader can prove this by substitution: the eigenvectors take the form $\frac{1}{\sqrt{r}}\sum_{m=0}^{r-1}\exp(\frac{-2\pi i m n}{r})\ket{x^k \mod N}$.} are a function of $r$:
\begin{equation}
e^{2i\pi k/r}\text{ for some integer }k
\end{equation}

The phase estimation algorithm can estimate $\theta=k/r$ to within a given error $\epsilon$: it returns $\widetilde\theta \in (\theta-\epsilon, \theta+\epsilon)$. We then need to minimize the error to a point where classical algorithms can recover $\theta$ from $\widetilde\theta$.

Because the candidates for $k/r$ are so close to one another (in the worst case, $1/N$ apart) and the number of gates is $O(1/\epsilon)$, direct application of the phase estimation algorithm is cost-prohibitive. We instead use a mathematical trick to increase accuracy at no additional cost.

Consider the family of unitary operators
\begin{equation}
U_a, U_{(a^2)}, U_{(a^4)}, U_{(a^8)}...
\end{equation}
All such operators $U_b$ are integer powers of $U_a$: it is easy to verify that if $b = a^n$ then $U_b = (U_a)^n$. For this reason they have the same eigenvectors; and despite being integer powers they are generally as easy/costly to implement as $U_a$, since one need only precompute $a^n \mod N$ by repeated squaring. Their eigenvalues, however, have far lower error than $U_a$: note that if $U_a$ has an eigenvalue $e^{i\phi}$, then $U_{(a^2)}$ has an eigenvalue $e^{2i\phi}$, $U_{(a^4)}$ has an eigenvalue $e^{4i\phi}$, and so on. The QPE will then estimate $\phi$, $2\phi$, $4\phi$... to within the same error $\epsilon$, thus reducing the error on $\phi$ to $\epsilon$, $\epsilon/2$, $\epsilon/4$...

It can be shown that for the purposes of determining $r$ it is sufficient to estimate a few randomly picked eigenvalues with a precision smaller than $1/N^2$, which corresponds to measuring the eigenvalues for all $U_b$ until $b=a^{(2^p)}$, $2^p \approx N^2$.

\section{Demonstration}
We now demonstrate the use of Shor's algorithm to decrypt a RSA key and thus read the contents of a communication encrypted with RSA. Specifically, we will use the implementation from IBM's Qiskit library.

Practical concerns require us to use extremely small keys ($N=40$ at most), as the resulting circuits are otherwise too large and can take several minutes or hours to compute: empirically, we observe that a circuit for $N=33$ takes 9 minutes on the powerful IBM QASM simulator.

%\subsection{\LaTeX-Specific Advice}

%Please don't use the \verb|{eqnarray}| equation environment. Use \verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|environment leaves unsightly spaces around relation symbols.

%\subsection{Identify the Headings}
%Headings, or heads, are organizational devices that guide the reader through 
%your paper. There are two types: component heads and text heads.

%Component heads identify the different components of your paper and are not 
%topically subordinate to each other. Examples include Acknowledgments and 
%References and, for these, the correct style to use is ``Heading 5''. Use 
%``figure caption'' for your Figure captions, and ``table head'' for your 
%table title. Run-in heads, such as ``Abstract'', will require you to apply a 
%style (in this case, italic) in addition to the style provided by the drop 
%down menu to differentiate the head from the text.

%Text heads organize the topics on a relational, hierarchical basis. For 
%example, the paper title is the primary text head because all subsequent 
%material relates and elaborates on this one topic. If there are two or more 
%sub-topics, the next level head (uppercase Roman numerals) should be used 
%and, conversely, if there are not at least two sub-topics, then no subheads 
%should be introduced.

%\subsection{Figures and Tables}
%\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
%bottom of columns. Avoid placing them in the middle of columns. Large 
%figures and tables may span across both columns. Figure captions should be 
%below the figures; table heads should appear above the tables. Insert 
%figures and tables after they are cited in the text. Use the abbreviation 
%``Fig.~\ref{fig}'', even at the beginning of a sentence.
%
%\begin{table}[htbp]
%\caption{Table Type Styles}
%\begin{center}
%\begin{tabular}{|c|c|c|c|}
%\hline
%\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
%\cline{2-4} 
%\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
%\hline
%copy& More table copy$^{\mathrm{a}}$& &  \\
%\hline
%\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
%\end{tabular}
%\label{tab1}
%\end{center}
%\end{table}
%
%\begin{figure}[htbp]
%\centerline{\includegraphics{fig1.png}}
%\caption{Example of a figure caption.}
%\label{fig}
%\end{figure}

%Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
%rather than symbols or abbreviations when writing Figure axis labels to 
%avoid confusing the reader. As an example, write the quantity 
%``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
%units in the label, present them within parentheses. Do not label axes only 
%with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
%\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
%quantities and units. For example, write ``Temperature (K)'', not 
%``Temperature/K''.

\begin{thebibliography}{00}
\bibitem{shor} P. W. Shor, "Algorithms for quantum computation: discrete logarithms and factoring", SIAM J.Sci.Statist.Comput. 26, 1997
\bibitem{rsa} R. Rivest, A. Shamir, L. Adleman, "A Method for Obtaining Digital Signatures and Public-Key Cryptosystems", Communications of the ACM 21, 1978
\bibitem{miller} G. L. Miller, "Riemann's hypothesis and tests for primality", J. Comput. System Sci., 1976
\bibitem{vbe} V. Vedral, A. Barenco, A. Ekert, "Quantum Networks for Elementary Arithmetic Operations", Physical Review A 54
\bibitem{ibm} IBM, "Shor's algorithm",\\https://quantum-computing.ibm.com/docs/guide/q-algos/shor-s-algorithm
\end{thebibliography}
\vspace{12pt}

\end{document}

### 2020-05-30 RSA.py
Add Python code

@@ -1,0 +1,60 @@
+from math import sqrt
+
+def gcd(a, b):
+    if b == 0:
+        return a
+    else:
+        return gcd(b, a % b)
+
+def mod_inverse(a, m):
+    for x in range(1, m):
+        if (a * x) % m == 1:
+            return x
+    return -1
+
+def isprime(n):
+    if n < 2:
+        return False
+    elif n == 2:
+        return True
+    else:
+        for i in range(1, int(sqrt(n)) + 1):
+            if n % i == 0:
+                return False
+    return True
+
+# Transforms a string into a sequence of values not greater than pq=33
+def serialize(plaintext):
+    words = []
+    for byte in bytes(plaintext, 'UTF-8'):
+        words.extend([byte & 0x1f, byte >> 5])
+    return words
+
+def deserialize(words):
+    plaintext = []
+    # Trick to read two words at a time. https://stackoverflow.com/a/16789817
+    it = iter(words)
+    for word in it:
+        plaintext.append(word + (next(it) << 5))
+    return plaintext
+
+def generate_keypair():
+    p = 11
+    q = 3
+    n = p * q
+    d = 7
+    e = 3
+
+    return ((e, n), (d, n))
+
+def encrypt(msg_plaintext, pubkey):
+    e, n = pubkey
+    msg_serialized = serialize(msg_plaintext)
+    msg_ciphertext = [pow(c, e, n) for c in msg_serialized]
+    return msg_ciphertext
+
+def decrypt(msg_ciphertext, privkey):
+    d, n = privkey
+    msg_serialized = [(pow(c, d, n)) for c in msg_ciphertext]
+    msg_plaintext = [chr(c) for c in deserialize(msg_serialized)]
+    return ''.join(msg_plaintext)

### 2020-05-30 client.py

@@ -1,0 +1,26 @@
+import socket
+import sys
+import RSA
+
+HOST, PORT = "localhost", 9999
+data = " ".join(sys.argv[1:])
+
+public, private = RSA.generate_keypair()
+
+# Create a socket (SOCK_STREAM means a TCP socket)
+with socket.socket(socket.AF_INET, socket.SOCK_STREAM) as sock:
+    # Connect to server and send data
+    sock.connect((HOST, PORT))
+    msg = data
+    encrypted_msg = RSA.encrypt(msg, public)
+    sock.sendall(bytes(encrypted_msg))
+    # sock.sendall(bytes(data + "\n", "utf-8"))
+
+    # Receive data from the server and shut down
+    indata = sock.recv(1024)
+    received = str(indata, "utf-8")
+    decrypted = RSA.decrypt(indata, private)
+    # received = RSA.decrypt(encrypted_msg, private)
+
+print("Sent:     {}".format(data))
+print("Received: {}".format(decrypted))

### 2020-05-30 quant.py

@@ -1,0 +1,26 @@
+from qiskit_fast_shor import TaggedDAG, Shor
+from qiskit import Aer, IBMQ
+
+IBMQ.load_account()
+
+a, N = 2, 21
+
+backend = Aer.get_backend('qasm_simulator')
+# provider = IBMQ.load_account()
+# backend = provider.get_backend('ibmq_qasm_simulator')
+
+shor = Shor(N, a, quantum_instance=backend)
+print("Constructing...")
+circuit = shor.construct_circuit()
+print("Drawing...")
+#if not isProfiler:
+#    print(circuit.draw())  # or circuit.draw(output='mpl') for a nicer looking diagram ;)
+print("Running...")
+if N == 33:
+    job_id = "5ecaeb4bd2d11d001a1aaf72"
+elif N == 15:
+    job_id = "5ecae5ed4f56e200131772af"
+else:
+    job_id = None
+res = shor.run(job_id=job_id)
+print(res)

### 2020-05-30 server.py

@@ -1,0 +1,33 @@
+import socketserver
+import RSA
+
+public, private = RSA.generate_keypair()
+
+class MyTCPHandler(socketserver.BaseRequestHandler):
+    """
+    The request handler class for our server.
+
+    It is instantiated once per connection to the server, and must
+    override the handle() method to implement communication to the
+    client.
+    """
+
+    def handle(self):
+        # self.request is the TCP socket connected to the client
+        self.data = self.request.recv(1024).strip()
+        print("{} wrote:".format(self.client_address[0]))
+        print(self.data)
+        msg = RSA.decrypt(self.data, private)
+        print(msg)
+        output = RSA.encrypt(msg.upper(), public)
+        # just send back the same data, but upper-cased
+        self.request.sendall(bytes(output))
+
+if __name__ == "__main__":
+    HOST, PORT = "localhost", 9999
+
+    # Create the server, binding to localhost on port 9999
+    with socketserver.TCPServer((HOST, PORT), MyTCPHandler) as server:
+        # Activate the server; this will keep running until you
+        # interrupt the program with Ctrl-C
+        server.serve_forever()

### 2020-05-30 sniff.py

@@ -1,0 +1,24 @@
+#! /usr/bin/env python3
+
+from scapy.all import sniff, TCP
+import RSA
+
+public, private = RSA.generate_keypair()
+
+packets_seen = []
+
+def custom_action(packet):
+    payload = packet[0][1][TCP].payload
+    if len(payload) == 0:
+        return
+    seq = packet[0][1][TCP].seq
+    if seq in packets_seen:
+        return
+    packets_seen.append(seq)
+    if packet[0][1].sport == 9999:
+        indicator = "> "
+    else:
+        indicator = "< "
+    return indicator + RSA.decrypt(bytes(payload), private)
+
+sniff(filter="tcp", prn=custom_action, iface="lo", store=0)

### 2020-05-31 paper/paper.tex
paper: Add RSA implementation

@@
 \documentclass[conference]{IEEEtran}
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
 \usepackage{cite}
@@
 We now demonstrate the use of Shor's algorithm to decrypt a RSA key and thus read the contents of a communication encrypted with RSA.
-Specifically, we will use the implementation from IBM's Qiskit library.
+Specifically, we will use the implementation contained in Qiskit, a mainstream open-source framework for quantum computing.
 
-Practical concerns require us to use extremely small keys ($N=40$ at most), as the resulting circuits are otherwise too large and can take several minutes or hours to compute: empirically, we observe that a circuit for $N=33$ takes 9 minutes on the powerful IBM QASM simulator.
+\subsection{RSA}
+Although RSA keys are almost universally 1024, 2048 or 3072 bits long, such sizes are computationally infeasible, and practical concerns require us to use extremely small keys (around $N=30$ at most).
+The resulting circuits are otherwise too large and can take several minutes or hours to compute: empirically, we observe that a circuit for $N=33$ is executed in 9 minutes on the powerful IBM QASM simulator.
+Needless to say, a key with $N<30$ provides no actual security as it can be factored by hand, and only serves as a demonstration in place of larger keys.
+
+Mainstream RSA implementations are designed with reasonable minimum key sizes: for instance, OpenSSL requires 384 bits or more, and will fail with an error for shorter keys.
+This requirement partly stems from the use of padding schemes, which add desirable security properties such as non-determinism (the same message encrypted several times will have several different encryptions; this is not true with plain RSA), preventing partial decryption, and others.
+As we only want to explore the feasibility of factoring the RSA key, such security properties are not of interest to us, and we can use a custom RSA implementation with tiny keys and no padding schemes.
+
+We devise a simple client-server application that simulates an email service.
+Users can log in with their username and password, and once logged in they can browse their email messages.
+It uses a simple cryptographic protocol that simulates TLS, where the server sends its public key to the client, which in turn sends an encrypted AES key (a "session key") allowing for secure two-way communication.
+The goal of this demonstration is to capture the public key and factor it, allowing a third party to decrypt messages intended for the server and snoop on the credentials and the email messages.
+
+\subsection{Shor}
 

### 2020-05-31 paper/paper.tex
paper: Add Shor improvement + application

@@
 \usepackage{graphicx}
+\usepackage{listings}
 \usepackage{physics}
@@
 
-\subsection{Order-finding subroutine}
+\subsection{Order-finding subroutine}\label{order-finding}
 We can further reduce the order-finding problem to the well-known problem of finding the eigenvalues of a unitary operator, which can be solved with the quantum phase estimation algorithm.
@@
 
-We devise a simple client-server application that simulates an email service.
+\subsection{Shor}
+We use the implementation of Shor's algorithm from the Qiskit library.
+The implementation uses the techniques outlined in section \ref{order-finding}, where the modular exponentiation circuit used to construct $U_b$ is derived in \cite{vbe}.
+
+We present a dramatic improvement upon this algorithm that brings the time spent constructing the circuit from 127 seconds (Qiskit's implementation at the time of writing) to 6 for $N=33$.
+The resulting circuit is identical and thus has the same execution time; this improvement merely makes the circuit construction faster.
+
+Simple line profiling shows that the Qiskit implementation spends a large amount of time "composing" subcircuits together (for instance, appending an IQFT circuit as part of the QPE routine).
+Delving into the library code shows that the composition of circuits is implemented by transforming the operands into DAGs\footnote{DAG: Directed Acyclic Graph.}, merging those, and then retransforming back into a circuit.
+We report an abridged version:
+
+\lstset{basicstyle=\ttfamily\footnotesize,breaklines=true}
+\begin{lstlisting}[language=Python]
+def compose(self, other):
+        dag_self = circuit_to_dag(self)
+        dag_other = circuit_to_dag(other)
+        dag_self.compose(dag_other)
+        return dag_to_circuit(dag_self)
+\end{lstlisting}
+
+Further profiling shows that the conversion from and to DAGs is very computationally intensive with respect to the other steps.
+The key intuition is that multiple compositions are therefore wasteful, as they spend a lot of time converting intermediate values back and forth; representing them as DAGs instead, only converting to and from DAGs respectively at the beginning and at the end of the algorithm, allows for much more efficient composition.
+In reality the composition takes additional arguments (most importantly the qubit indices on which to compose), which need to be stored along with the DAG - we call this object a "tagged DAG".
+This simple modification then allows to construct the circuit correctly with dramatic speed improvements.
+
+This improvement was discovered independently by Thomas Metcalfe, who submitted it in a slightly different form on May 25 as part of pull request \#975 to Qiskit Aqua.
+As the PR is not yet merged at the time of writing, we have released our implementation \cite{github-repo} as a separate repository.
+
+\subsection{Application}
+We develop a simple client-server application that simulates an email service.
 Users can log in with their username and password, and once logged in they can browse their email messages.
@@
 The goal of this demonstration is to capture the public key and factor it, allowing a third party to decrypt messages intended for the server and snoop on the credentials and the email messages.
-
-\subsection{Shor}
 
@@
 \bibitem{ibm} IBM, "Shor's algorithm",\\https://quantum-computing.ibm.com/docs/guide/q-algos/shor-s-algorithm
+\bibitem{github-repo} G. Muscarello, https://github.com/CapacitorSet/qiskit-fast-shor
 \end{thebibliography}

### 2020-05-31 RSA.py
code: Refactor user interface

@@ -23,24 +23,22 @@ def isprime(n):
                 return False
     return True
 
-# Transforms a string into a sequence of values not greater than pq=33
+# Transforms a string into a sequence of values not greater than 8
 def serialize(plaintext):
     words = []
     for byte in bytes(plaintext, 'UTF-8'):
-        words.extend([byte & 0x1f, byte >> 5])
+        words.extend([byte & 7, (byte >> 3) & 7, byte >> 6])
     return words
 
 def deserialize(words):
     plaintext = []
-    # Trick to read two words at a time. https://stackoverflow.com/a/16789817
+    # Trick to read N words at a time. https://stackoverflow.com/a/16789817
     it = iter(words)
     for word in it:
-        plaintext.append(word + (next(it) << 5))
+        plaintext.append(word + (next(it) << 3) + (next(it) << 6))
     return plaintext
 
-def generate_keypair():
-    p = 11
-    q = 3
+def generate_keypair(p, q):
     n = p * q
     d = 7
     e = 3
@@ -49,9 +47,11 @@ def generate_keypair():
 
 def encrypt(msg_plaintext, pubkey):
     e, n = pubkey
+    # We encrypt one byte at a time, so as not to exceed N=pq as long as we
+    # don't pick an absurdly tiny value
     msg_serialized = serialize(msg_plaintext)
     msg_ciphertext = [pow(c, e, n) for c in msg_serialized]
-    return msg_ciphertext
+    return bytes(msg_ciphertext)
 
 def decrypt(msg_ciphertext, privkey):
     d, n = privkey

### 2020-05-31 client.py

@@ -1,26 +1,42 @@
+import logging
+import re
+import RSA
 import socket
 import sys
-import RSA
 
 HOST, PORT = "localhost", 9999
-data = " ".join(sys.argv[1:])
+logging.basicConfig(format='%(asctime)s [%(levelname)s] %(message)s', datefmt='%m/%d/%Y %H:%M:%S', level=logging.DEBUG)
 
-public, private = RSA.generate_keypair()
+public, private = RSA.generate_keypair(3, 11)
+pubkey_pattern = re.compile("pubkey: e=([0-9]+), n=([0-9]+)")
 
-# Create a socket (SOCK_STREAM means a TCP socket)
 with socket.socket(socket.AF_INET, socket.SOCK_STREAM) as sock:
     # Connect to server and send data
     sock.connect((HOST, PORT))
-    msg = data
-    encrypted_msg = RSA.encrypt(msg, public)
-    sock.sendall(bytes(encrypted_msg))
-    # sock.sendall(bytes(data + "\n", "utf-8"))
+    logging.info("Connected to {}:{}".format(HOST, PORT))
+
+    # Receive and parse pubkey
+    pubkeydata = sock.recv(1024)
+    pubkey_matches = pubkey_pattern.match(str(pubkeydata, 'utf-8'))
+    pubkey = (int(pubkey_matches.group(1)), int(pubkey_matches.group(2)))
+    logging.debug("Public key: {}".format(pubkey))
+
+    print("Enter your credentials to log in.")
+    print("")
+
+    msg = input("    Email: ")
+    encrypted_msg = RSA.encrypt(msg, pubkey)
+    logging.debug("Sent {}".format(encrypted_msg))
+    sock.sendall(encrypted_msg)
+    msg = input("    Password: ")
+    encrypted_msg = RSA.encrypt(msg, pubkey)
+    logging.debug("Sent {}".format(encrypted_msg))
+    sock.sendall(encrypted_msg)
+    print("")
+    print("Logged in successfully! Here are your emails:")
+    print("")
 
     # Receive data from the server and shut down
     indata = sock.recv(1024)
-    received = str(indata, "utf-8")
     decrypted = RSA.decrypt(indata, private)
-    # received = RSA.decrypt(encrypted_msg, private)
-
-print("Sent:     {}".format(data))
-print("Received: {}".format(decrypted))
+    logging.debug("Received {}".format(decrypted))

### 2020-05-31 server.py

@@ -1,7 +1,10 @@
-import socketserver
+import logging
 import RSA
+import socketserver
 
-public, private = RSA.generate_keypair()
+logging.basicConfig(format='%(asctime)s [%(levelname)s] %(message)s', datefmt='%m/%d/%Y %H:%M:%S', level=logging.DEBUG)
+
+public, private = RSA.generate_keypair(3, 11)
 
 class MyTCPHandler(socketserver.BaseRequestHandler):
     """
@@ -13,21 +16,26 @@ class MyTCPHandler(socketserver.BaseRequestHandler):
     """
 
     def handle(self):
-        # self.request is the TCP socket connected to the client
-        self.data = self.request.recv(1024).strip()
-        print("{} wrote:".format(self.client_address[0]))
-        print(self.data)
-        msg = RSA.decrypt(self.data, private)
-        print(msg)
-        output = RSA.encrypt(msg.upper(), public)
-        # just send back the same data, but upper-cased
-        self.request.sendall(bytes(output))
+        logging.info("New connection from {}".format(self.client_address[0]))
 
-if __name__ == "__main__":
-    HOST, PORT = "localhost", 9999
+        # Send the public key
+        pubkey_message = "pubkey: e={}, n={}".format(public[0], public[1])
+        logging.debug("Sent: {}".format(pubkey_message))
+        self.request.sendall(bytes(pubkey_message, 'utf-8'))
 
-    # Create the server, binding to localhost on port 9999
-    with socketserver.TCPServer((HOST, PORT), MyTCPHandler) as server:
-        # Activate the server; this will keep running until you
-        # interrupt the program with Ctrl-C
-        server.serve_forever()
+        # Read the username and discard it
+        self.request.recv(1024)
+        # Read the password and discard it
+        self.request.recv(1024)
+
+        output = RSA.encrypt("henlo", public)
+        logging.debug("Sent: {}".format(output))
+        self.request.sendall(output)
+        self.request.close()
+
+HOST, PORT = "localhost", 9999
+
+# Create the server, binding to localhost on port 9999
+with socketserver.TCPServer((HOST, PORT), MyTCPHandler) as server:
+    logging.info("Listening on {}".format(HOST, PORT))
+    server.serve_forever()

### 2020-06-02 paper/paper.tex
paper: Add mod exp + misc

@@
 \subsection{Order-finding subroutine}\label{order-finding}
-We can further reduce the order-finding problem to the well-known problem of finding the eigenvalues of a unitary operator, which can be solved with the quantum phase estimation algorithm.
+The key insight in Shor's algorithm is that the order-finding problem can be expressed in terms of finding the eigenvalues of a unitary operator, a problem which can be solved with the quantum phase estimation algorithm in $O((\log N)^3)$, i.e.
+linearly in the number of bits of $N$.
+For comparison, the best classical algorithm for factoring has a complexity of $O(e^{(\log N)^{1/3}(\log\log N)^{2/3}})$.
+
 Shor exploits the unitary operator
@@
 It can be shown that for the purposes of determining $r$ it is sufficient to estimate a few randomly picked eigenvalues with a precision smaller than $1/N^2$, which corresponds to measuring the eigenvalues for all $U_b$ until $b=a^{(2^p)}$, $2^p \approx N^2$.
+
+\subsection{Modular exponentiation}
+The modular exponentiation procedure is at the heart of Shor's algorithm, and can be implemented in several ways.
+Notably, any classical computation (thus including modular exponentiation) can be expressed in terms of Toffoli gates, as they are universal for Boolean functions --- for an example of such a general approach, see \cite{toffoli}.
+However, in literature we can find specialized circuits for modular exponentiation, the first being described in a paper \cite{vbe} by Vedral, Barenco and Ekert and still used today in Qiskit's implementation of Shor's algorithm.
 
@@
 \subsection{Application}
-We develop a simple client-server application that simulates an email service.
+We develop a simple client-server application that emulates an email service.
 Users can log in with their username and password, and once logged in they can browse their email messages.
@@
 \begin{thebibliography}{00}
-\bibitem{shor} P. W. Shor, "Algorithms for quantum computation: discrete logarithms and factoring", SIAM J.Sci.Statist.Comput. 26, 1997
-\bibitem{rsa} R. Rivest, A. Shamir, L. Adleman, "A Method for Obtaining Digital Signatures and Public-Key Cryptosystems", Communications of the ACM 21, 1978
-\bibitem{miller} G. L. Miller, "Riemann's hypothesis and tests for primality", J. Comput. System Sci., 1976
+\bibitem{shor} P. W. Shor, "Algorithms for quantum computation: discrete logarithms and factoring", SIAM J.Sci.Statist.Comput. 26
+\bibitem{rsa} R. Rivest, A. Shamir, L. Adleman, "A Method for Obtaining Digital Signatures and Public-Key Cryptosystems", Communications of the ACM 21
+\bibitem{miller} G. L. Miller, "Riemann's hypothesis and tests for primality", J. Comput. System Sci.
 \bibitem{vbe} V. Vedral, A. Barenco, A. Ekert, "Quantum Networks for Elementary Arithmetic Operations", Physical Review A 54
+\bibitem{toffoli} D. Maslov, G. W. Dueck, D. M. Miller, "Toffoli network synthesis with templates," IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems
 \bibitem{ibm} IBM, "Shor's algorithm",\\https://quantum-computing.ibm.com/docs/guide/q-algos/shor-s-algorithm

### 2020-06-02 RSA.py
code: Add AES session key

@@ -26,7 +26,7 @@ def isprime(n):
 # Transforms a string into a sequence of values not greater than 8
 def serialize(plaintext):
     words = []
-    for byte in bytes(plaintext, 'UTF-8'):
+    for byte in plaintext:
         words.extend([byte & 7, (byte >> 3) & 7, byte >> 6])
     return words
 
@@ -47,14 +47,25 @@ def generate_keypair(p, q):
 
 def encrypt(msg_plaintext, pubkey):
     e, n = pubkey
-    # We encrypt one byte at a time, so as not to exceed N=pq as long as we
-    # don't pick an absurdly tiny value
+    # We encrypt 3 bits at a time, so as not to exceed N=pq as long as we
+    # don't pick an absurdly tiny value. But assert it anyway.
+    assert n >= 8
     msg_serialized = serialize(msg_plaintext)
     msg_ciphertext = [pow(c, e, n) for c in msg_serialized]
     return bytes(msg_ciphertext)
 
+def encrypt_str(msg_plaintext, pubkey):
+    return encrypt(bytes(msg_plaintext, 'UTF-8'), pubkey)
+
 def decrypt(msg_ciphertext, privkey):
     d, n = privkey
+    assert n >= 8
+    msg_serialized = [(pow(c, d, n)) for c in msg_ciphertext]
+    return bytes([c for c in deserialize(msg_serialized)])
+
+def decrypt_str(msg_ciphertext, privkey):
+    d, n = privkey
+    assert n >= 8
     msg_serialized = [(pow(c, d, n)) for c in msg_ciphertext]
     msg_plaintext = [chr(c) for c in deserialize(msg_serialized)]
     return ''.join(msg_plaintext)

### 2020-06-02 client.py

@@ -1,3 +1,6 @@
+from Crypto.Cipher import AES
+from Crypto.Util.Padding import pad, unpad
+from Crypto.Random import get_random_bytes
 import logging
 import re
 import RSA
@@ -7,7 +10,6 @@ import sys
 HOST, PORT = "localhost", 9999
 logging.basicConfig(format='%(asctime)s [%(levelname)s] %(message)s', datefmt='%m/%d/%Y %H:%M:%S', level=logging.DEBUG)
 
-public, private = RSA.generate_keypair(3, 11)
 pubkey_pattern = re.compile("pubkey: e=([0-9]+), n=([0-9]+)")
 
 with socket.socket(socket.AF_INET, socket.SOCK_STREAM) as sock:
@@ -21,22 +23,38 @@ with socket.socket(socket.AF_INET, socket.SOCK_STREAM) as sock:
     pubkey = (int(pubkey_matches.group(1)), int(pubkey_matches.group(2)))
     logging.debug("Public key: {}".format(pubkey))
 
+    # Generate AES IV & session key
+    session_key = get_random_bytes(16)
+    logging.debug("Session key: " + session_key.hex())
+    encrypted_session_key = RSA.encrypt(session_key, pubkey)
+    sock.sendall(encrypted_session_key)
+    cipher = AES.new(session_key, AES.MODE_CBC)
+    # The IV should not be reused in the real world! But this is a demo about
+    # factoring RSA keys in TLS, so we can ignore other cryptographic concerns.
+    iv = cipher.iv
+    logging.debug("AES IV: " + iv.hex())
+    sock.sendall(iv)
+
+    # All communication from now on will be encrypted with the AES session key.
+
     print("Enter your credentials to log in.")
     print("")
 
-    msg = input("    Email: ")
-    encrypted_msg = RSA.encrypt(msg, pubkey)
-    logging.debug("Sent {}".format(encrypted_msg))
-    sock.sendall(encrypted_msg)
-    msg = input("    Password: ")
-    encrypted_msg = RSA.encrypt(msg, pubkey)
-    logging.debug("Sent {}".format(encrypted_msg))
-    sock.sendall(encrypted_msg)
+    email = input("    Email: ")
+    encrypted_email = cipher.encrypt(pad(bytes(email, 'UTF-8'), AES.block_size))
+    logging.debug("Sent {}".format(encrypted_email))
+    sock.sendall(encrypted_email)
+    password = input("    Password: ")
[…]

### 2020-06-02 server.py

@@ -1,3 +1,5 @@
+from Crypto.Cipher import AES
+from Crypto.Util.Padding import pad, unpad
 import logging
 import RSA
 import socketserver
@@ -23,13 +25,26 @@ class MyTCPHandler(socketserver.BaseRequestHandler):
         logging.debug("Sent: {}".format(pubkey_message))
         self.request.sendall(bytes(pubkey_message, 'utf-8'))
 
-        # Read the username and discard it
-        self.request.recv(1024)
-        # Read the password and discard it
-        self.request.recv(1024)
+        # Read the AES IV & session key
+        encrypted_session_key = self.request.recv(1024)
+        session_key = RSA.decrypt(encrypted_session_key, private)
+        logging.debug("Session key: " + session_key.hex())
+        iv = self.request.recv(16)
+        logging.debug("AES IV: " + iv.hex())
+        cipher = AES.new(session_key, AES.MODE_CBC, iv)
 
-        output = RSA.encrypt("henlo", public)
-        logging.debug("Sent: {}".format(output))
+        # Read the credentials. Pretend logins are always successful.
+        encrypted_email = self.request.recv(1024)
+        email = str(unpad(cipher.decrypt(encrypted_email), AES.block_size), 'UTF-8')
+        encrypted_password = self.request.recv(1024)
+        password = str(unpad(cipher.decrypt(encrypted_password), AES.block_size), 'UTF-8')
+        logging.info("New login: email={}, password={}".format(email, password))
+
+        # Workaround to force the crypto lib to play nice
+        cipher._next = [cipher.encrypt, cipher.decrypt]
+        # Send the list of emails
+        output = cipher.encrypt(pad(bytes("henlo", 'UTF-8'), AES.block_size))
+        logging.debug("Sent: " + output.hex())
         self.request.sendall(output)
         self.request.close()
 

### 2020-06-03 client.py
code: Move factoring to quant.py

@@ -8,7 +8,11 @@ import socket
 import sys
 
 HOST, PORT = "localhost", 9999
-logging.basicConfig(format='%(asctime)s [%(levelname)s] %(message)s', datefmt='%m/%d/%Y %H:%M:%S', level=logging.DEBUG)
+if "--debug" in sys.argv:
+    loglevel = logging.DEBUG
+else:
+    loglevel = logging.INFO
+logging.basicConfig(format='%(asctime)s [%(levelname)s] %(message)s', datefmt='%m/%d/%Y %H:%M:%S', level=loglevel)
 
 pubkey_pattern = re.compile("pubkey: e=([0-9]+), n=([0-9]+)")
 
@@ -42,11 +46,9 @@ with socket.socket(socket.AF_INET, socket.SOCK_STREAM) as sock:
 
     email = input("    Email: ")
     encrypted_email = cipher.encrypt(pad(bytes(email, 'UTF-8'), AES.block_size))
-    logging.debug("Sent {}".format(encrypted_email))
     sock.sendall(encrypted_email)
     password = input("    Password: ")
     encrypted_password = cipher.encrypt(pad(bytes(password, 'UTF-8'), AES.block_size))
-    logging.debug("Sent {}".format(encrypted_password))
     sock.sendall(encrypted_password)
     print("")
     print("Logged in successfully! Here are your emails:")
@@ -57,4 +59,4 @@ with socket.socket(socket.AF_INET, socket.SOCK_STREAM) as sock:
     # Receive data from the server and shut down
     indata = sock.recv(1024)
     decrypted = str(unpad(cipher.decrypt(indata), AES.block_size), 'UTF-8')
-    logging.debug("Received {}".format(decrypted))
+    print(decrypted)

### 2020-06-03 quant.py

@@ -1,4 +1,4 @@
-from qiskit_fast_shor import TaggedDAG, Shor
+from qiskit_fast_shor import Shor
 from qiskit import Aer, IBMQ
 
 IBMQ.load_account()
@@ -9,18 +9,16 @@ backend = Aer.get_backend('qasm_simulator')
 # provider = IBMQ.load_account()
 # backend = provider.get_backend('ibmq_qasm_simulator')
 
-shor = Shor(N, a, quantum_instance=backend)
-print("Constructing...")
-circuit = shor.construct_circuit()
-print("Drawing...")
-#if not isProfiler:
-#    print(circuit.draw())  # or circuit.draw(output='mpl') for a nicer looking diagram ;)
-print("Running...")
 if N == 33:
     job_id = "5ecaeb4bd2d11d001a1aaf72"
 elif N == 15:
     job_id = "5ecae5ed4f56e200131772af"
 else:
     job_id = None
-res = shor.run(job_id=job_id)
-print(res)
+shor = Shor(N, a, quantum_instance=backend, job_id=job_id)
+print("Constructing...")
+circuit = shor.construct_circuit()
+print("Running...")
+res = shor.run()
+p, q = res["factors"][0]
+print("p, q = {}, {}".format(p, q))

### 2020-06-03 server.py

@@ -3,10 +3,16 @@ from Crypto.Util.Padding import pad, unpad
 import logging
 import RSA
 import socketserver
+import sys
 
-logging.basicConfig(format='%(asctime)s [%(levelname)s] %(message)s', datefmt='%m/%d/%Y %H:%M:%S', level=logging.DEBUG)
+if "--debug" in sys.argv:
+    loglevel = logging.DEBUG
+else:
+    loglevel = logging.INFO
 
-public, private = RSA.generate_keypair(3, 11)
+logging.basicConfig(format='%(asctime)s [%(levelname)s] %(message)s', datefmt='%m/%d/%Y %H:%M:%S', level=loglevel)
+
+public, private = RSA.generate_keypair(3, 5)
 
 class MyTCPHandler(socketserver.BaseRequestHandler):
     """
@@ -43,7 +49,11 @@ class MyTCPHandler(socketserver.BaseRequestHandler):
         # Workaround to force the crypto lib to play nice
         cipher._next = [cipher.encrypt, cipher.decrypt]
         # Send the list of emails
-        output = cipher.encrypt(pad(bytes("henlo", 'UTF-8'), AES.block_size))
+        emails = \
+            "    <From maurizio.zamboni@polito.it> PolitOpenDays\n" +\
+            "    <From rettore@polito.it> Nuove indicazioni per le attività didattiche\n" +\
+            "    <From anna.carbone@polito.it> Your IICQ exam results"
+        output = cipher.encrypt(pad(bytes(emails, 'UTF-8'), AES.block_size))
         logging.debug("Sent: " + output.hex())
         self.request.sendall(output)
         self.request.close()
@@ -52,5 +62,5 @@ HOST, PORT = "localhost", 9999
 
 # Create the server, binding to localhost on port 9999
 with socketserver.TCPServer((HOST, PORT), MyTCPHandler) as server:
-    logging.info("Listening on {}".format(HOST, PORT))
+    logging.info("Listening on {}:{}".format(HOST, PORT))
     server.serve_forever()

### 2020-06-03 sniff.py

@@ -1,9 +1,113 @@
-#! /usr/bin/env python3
-
+from Crypto.Cipher import AES
+from Crypto.Random import get_random_bytes
+from Crypto.Util.Padding import pad, unpad
+from qiskit_fast_shor import Shor
+from qiskit import Aer, IBMQ
 from scapy.all import sniff, TCP
+import logging
+import re
 import RSA
+import socket
+import sys
 
-public, private = RSA.generate_keypair()
+# Defaulting level to logging.WARN helps us disable logging in Qiskit code
+logging.basicConfig(format='%(asctime)s [%(levelname)s] %(message)s', datefmt='%m/%d/%Y %H:%M:%S', level=logging.WARN)
+logger = logging.getLogger('simple_example')
+if "--debug" in sys.argv:
+    logger.setLevel(logging.DEBUG)
+else:
+    logger.setLevel(logging.INFO)
+
+class SniffingFSM:
+    state = "INIT"
+
+    def ingest(self, data, sourceIsServer):
+        if self.state == "INIT":
+            assert sourceIsServer
+            pubkey_pattern = re.compile("pubkey: e=([0-9]+), n=([0-9]+)")
+            pubkey_matches = pubkey_pattern.match(str(data, 'utf-8'))
+            self.pubkey = (int(pubkey_matches.group(1)), int(pubkey_matches.group(2)))
+            logger.info("Public key found: {}".format(self.pubkey))
+            self.state = "AWAIT_SESSION_KEY"
+        elif self.state == "AWAIT_SESSION_KEY":
+            assert not sourceIsServer
+            self.encrypted_session_key = data
+            logger.debug("Encrypted session key: " + self.encrypted_session_key.hex())
+            self.state = "AWAIT_IV"
+        elif self.state == "AWAIT_IV":
+            assert not sourceIsServer
+            self.iv = data
+            logger.debug("AES IV: " + self.iv.hex())
+            self.state = "AWAIT_EMAIL"
+        elif self.state == "AWAIT_EMAIL":
+            assert not sourceIsServer
+            self.encrypted_email = data
+            logger.debug("Encrypted email: " + self.encrypted_email.hex())
+            self.state = "AWAIT_PASSWORD"
+        elif self.state == "AWAIT_PASSWORD":
+            assert not sourceIsServer
+            self.encrypted_password = data
+            logger.debug("Encrypted password: " + self.encrypted_password.hex())
+            self.state = "AWAIT_EMAILS"
+        elif self.state == "AWAIT_EMAILS":
[…]

### 2020-06-03 RSA.py
code: Implement search for modular inverse

@@ -1,4 +1,5 @@
 from math import sqrt
+import random
 
 def gcd(a, b):
     if b == 0:
@@ -40,10 +41,19 @@ def deserialize(words):
 
 def generate_keypair(p, q):
     n = p * q
-    d = 7
-    e = 3
+    if p*q == 15:
+        d = 7
+        e = 3
+        return ((e, n), (d, n))
 
-    return ((e, n), (d, n))
+    phi = (p - 1) * (q - 1)
+    for e in range(1, phi):
+        g = gcd(e, phi)
+        d = mod_inverse(e, phi)
+        if g == 1 and e != d:
+            return ((e, n), (d, n))
+
+    raise Exception("No modular inverse exists for p, q = {}, {}".format(p, q))
 
 def encrypt(msg_plaintext, pubkey):
     e, n = pubkey

### 2020-06-03 RSA.py
code: Remove e!=d check in RSA keygen

@@ -41,19 +41,14 @@ def deserialize(words):
 
 def generate_keypair(p, q):
     n = p * q
-    if p*q == 15:
-        d = 7
-        e = 3
-        return ((e, n), (d, n))
-
     phi = (p - 1) * (q - 1)
-    for e in range(1, phi):
+    for e in range(2, phi):
         g = gcd(e, phi)
         d = mod_inverse(e, phi)
-        if g == 1 and e != d:
+        if g == 1:
             return ((e, n), (d, n))
 
-    raise Exception("No modular inverse exists for p, q = {}, {}".format(p, q))
+    raise Exception("No modular inverse found for p, q = {}, {}".format(p, q))
 
 def encrypt(msg_plaintext, pubkey):
     e, n = pubkey

### 2020-06-03 paper/paper.tex
paper: Add screenshots+results, misc finishing touches

@@
 \usepackage{physics}
+\usepackage{caption}
+\usepackage{stfloats}
+
 \begin{document}
@@
 A mathematical description of RSA is out of scope for this paper, and can be found in \cite{rsa}.
-For the purposes of this paper, the cryptosystem can be thought of as a private key $A = \{p, q\}$, where $p$ and $q$ are primes known only to the receiver, and a public key $n=pq$, which can be disseminated.
+For the purposes of this paper, the cryptosystem can be thought of as a private key $\{p, q\}$, where $p$ and $q$ are primes known only to the receiver, and a public key $N=pq$, which can be disseminated.
 The public key allows any third party to encrypt messages, and the private key allows the receiver to decrypt messages intended for him.
@@
 \begin{itemize}
-\item $N$ and $a$ have some common prime factors, in which case $p=\gcd(N, a)$ returns one prime and $N/p$ returns the other;
+\item $N$ and $a$ have a common prime factor, in which case $p=\gcd(N, a)$ returns one prime and $N/p$ returns the other;
 \item let $r$ be the period defined above, then at least one of $p, q = \gcd(N, a^{r/2}\pm 1)$ are factors of $N$;
@@
 The phase estimation algorithm can estimate $\theta=k/r$ to within a given error $\epsilon$: it returns $\widetilde\theta \in (\theta-\epsilon, \theta+\epsilon)$.
-We then need to minimize the error to a point where classical algorithms can recover $\theta$ from $\widetilde\theta$.
+We then need to minimize the error to a point where classical algorithms (in this case, continued fraction expansion) can recover $\theta$ from $\widetilde\theta$.
 
@@
 All such operators $U_b$ are integer powers of $U_a$: it is easy to verify that if $b = a^n$ then $U_b = (U_a)^n$.
-For this reason they have the same eigenvectors; and despite being integer powers they are generally as easy/costly to implement as $U_a$, since one need only precompute $a^n \mod N$ by repeated squaring.
+For this reason they have the same eigenvectors, but despite being integer powers they are only as hard to implement as $U_a$, since one need only precompute $a^n \mod N$ by repeated squaring.
 Their eigenvalues, however, have far lower error than $U_a$: note that if $U_a$ has an eigenvalue $e^{i\phi}$, then $U_{(a^2)}$ has an eigenvalue $e^{2i\phi}$, $U_{(a^4)}$ has an eigenvalue $e^{4i\phi}$, and so on.
@@
 \subsection{RSA}
-Although RSA keys are almost universally 1024, 2048 or 3072 bits long, such sizes are computationally infeasible, and practical concerns require us to use extremely small keys (around $N=30$ at most).
-The resulting circuits are otherwise too large and can take several minutes or hours to compute: empirically, we observe that a circuit for $N=33$ is executed in 9 minutes on the powerful IBM QASM simulator.
-Needless to say, a key with $N<30$ provides no actual security as it can be factored by hand, and only serves as a demonstration in place of larger keys.
+RSA keys are typically 1024 or 2048 bits long, with some being 3072 or 4096 bits long.
+However, factoring such large keys with Shor's algorithm is computationally infeasible, and practical concerns require us to use extremely small keys (around $N=30$ at most).
+The resulting circuits are otherwise too large and can take several minutes or hours to compute: empirically, we observe that a circuit for $N=33$ is executed in 10 minutes on the powerful IBM QASM simulator.
+Needless to say, such small keys provide no actual security as they can be factored by hand, and only serve as a demonstration in place of larger keys.
 
@@
 This requirement partly stems from the use of padding schemes, which add desirable security properties such as non-determinism (the same message encrypted several times will have several different encryptions; this is not true with plain RSA), preventing partial decryption, and others.
-As we only want to explore the feasibility of factoring the RSA key, such security properties are not of interest to us, and we can use a custom RSA implementation with tiny keys and no padding schemes.
+As we only want to explore the feasibility of factoring the RSA key, such security properties are not of interest to us, and we can use a custom RSA implementation with tiny keys and no padding scheme.
 
@@
 
-We present a dramatic improvement upon this algorithm that brings the time spent constructing the circuit from 127 seconds (Qiskit's implementation at the time of writing) to 6 for $N=33$.
+We present a dramatic improvement upon this algorithm that brings the time spent constructing the circuit from 127 seconds (using Qiskit's implementation at the time of writing) to 6 seconds for $N=33$.
 The resulting circuit is identical and thus has the same execution time; this improvement merely makes the circuit construction faster.
 
-Simple line profiling shows that the Qiskit implementation spends a large amount of time "composing" subcircuits together (for instance, appending an IQFT circuit as part of the QPE routine).
+Simple line profiling shows that the Qiskit implementation spends a large amount of time composing subcircuits together (for instance, appending an IQFT circuit as part of the QPE routine).
 Delving into the library code shows that the composition of circuits is implemented by transforming the operands into DAGs\footnote{DAG: Directed Acyclic Graph.}, merging those, and then retransforming back into a circuit.
-We report an abridged version:
+We report an abridged version of the method:
 
@@
 Further profiling shows that the conversion from and to DAGs is very computationally intensive with respect to the other steps.
-The key intuition is that multiple compositions are therefore wasteful, as they spend a lot of time converting intermediate values back and forth; representing them as DAGs instead, only converting to and from DAGs respectively at the beginning and at the end of the algorithm, allows for much more efficient composition.
+The key intuition is that sequential compositions are therefore wasteful, as they spend a lot of time converting intermediate values back and forth; representing them as DAGs instead, only converting to and from DAGs respectively at the beginning and at the end of the algorithm, allows for much more efficient composition.
 In reality the composition takes additional arguments (most importantly the qubit indices on which to compose), which need to be stored along with the DAG - we call this object a "tagged DAG".
@@
 This improvement was discovered independently by Thomas Metcalfe, who submitted it in a slightly different form on May 25 as part of pull request \#975 to Qiskit Aqua.
-As the PR is not yet merged at the time of writing, we have released our implementation \cite{github-repo} as a separate repository.
+As the PR is not yet merged at the time of writing, we have released our implementation \cite{github-repo-shor} as a separate repository.
 
@@
 
-%\subsection{\LaTeX-Specific Advice}
+We have released the code for the demonstration, together with this paper, as a public Git repository \cite{github-repo-main}.
 
-%Please don't use the \verb|{eqnarray}| equation environment. Use \verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|environment leaves unsightly spaces around relation symbols.
+\section{Results and conclusions}
+We demonstrate that Shor's algorithm can be used to factor RSA keys and compromise encrypted channels. We present three cases:
+\begin{itemize}
+\item $N=15$, factored on a local simulator (Aer backend) in a few seconds;
+\item $N=21$, factored on the IBM QASM simulator in 40 seconds;
+\item $N=33$, which gave inconclusive results after approximately 10 minutes on the IBM QASM simulator.
+\end{itemize}
 
-%\subsection{Identify the Headings}
-%Headings, or heads, are organizational devices that guide the reader through 
-%your paper. There are two types: component heads and text heads.
+We notice that with the increase of $N$ the circuit depth and the execution times rise greatly, making local simulation impractical after a certain point.
+However, even powerful simulators like the one provided by IBM struggle to factor even modest values of $N$, which in turn are extremely tiny in comparison to keys used in the real world (the smaller ones being 1024 bit long).
 
-%Component heads identify the different components of your paper and are not 
-%topically subordinate to each other. Examples include Acknowledgments and 
-%References and, for these, the correct style to use is ``Heading 5''. Use 
-%``figure caption'' for your Figure captions, and ``table head'' for your 
-%table title. Run-in heads, such as ``Abstract'', will require you to apply a 
-%style (in this case, italic) in addition to the style provided by the drop 
-%down menu to differentiate the head from the text.
+While performance issues could in theory be addressed with real quantum computers with sufficiently many qubits, we also observe that the demonstration often fails for $N=33$.
+We attribute this to the large amount of noise and decoherence accumulated in the computation.
 
-%Text heads organize the topics on a relational, hierarchical basis. For 
-%example, the paper title is the primary text head because all subsequent 
-%material relates and elaborates on this one topic. If there are two or more 
-%sub-topics, the next level head (uppercase Roman numerals) should be used 
-%and, conversely, if there are not at least two sub-topics, then no subheads 
-%should be introduced.
+Overall, we find that Shor's algorithm is a simple and well-studied method to solve the factoring problem, but at the current time it is vastly unfeasible as a tool against real RSA keys due to the limits of current quantum computing technology.
 
-%\subsection{Figures and Tables}
-%\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
-%bottom of columns. Avoid placing them in the middle of columns. Large 
-%figures and tables may span across both columns. Figure captions should be 
-%below the figures; table heads should appear above the tables. Insert 
-%figures and tables after they are cited in the text. Use the abbreviation 
-%``Fig.~\ref{fig}'', even at the beginning of a sentence.
-%
-%\begin{table}[htbp]
-%\caption{Table Type Styles}
-%\begin{center}
-%\begin{tabular}{|c|c|c|c|}
-%\hline
-%\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
-%\cline{2-4} 
-%\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
-%\hline
-%copy& More table copy$^{\mathrm{a}}$& &  \\
-%\hline
-%\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
-%\end{tabular}
-%\label{tab1}
-%\end{center}
-%\end{table}
-%
-%\begin{figure}[htbp]
-%\centerline{\includegraphics{fig1.png}}
-%\caption{Example of a figure caption.}
-%\label{fig}
-%\end{figure}
+\begin{figure*}[b]
+   \centering
+   \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{2020-06-03_20-38.png}
+   \caption{A demonstration of the attack on the public key $e=3$, $N=15$.
+The algorithm was executed on a local simulator (Aer backend); the timestamps show that the factorization was carried out in a few seconds.\\Top left: the client interface.
+Top right: the server interface.
+Bottom: the attacker interface.}
+\end{figure*}
 
-%Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
-%rather than symbols or abbreviations when writing Figure axis labels to 
-%avoid confusing the reader. As an example, write the quantity 
-%``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
-%units in the label, present them within parentheses. Do not label axes only 
-%with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
-%\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
-%quantities and units. For example, write ``Temperature (K)'', not 
-%``Temperature/K''.
+\begin{figure*}[t]
+   \centering
+   \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{2020-06-03_23-29.png}
+   \caption{A demonstration of the attack on the public key $e=3$, $N=21$. The algorithm was executed on the IBM QASM simulator.}
+\end{figure*}
+
+\begin{figure*}[t]
+   \centering
+   \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{2020-06-03_20-54.png}
+   \caption{A demonstration of the attack on the public key $e=3$, $N=33$. The algorithm was executed on the IBM QASM simulator, and gave inconclusive results.}
+\end{figure*}
+
+\begin{figure*}[t]
+   \centering
+   \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{2020-06-03_20-56.png}
+   \caption{Timings for factorizing $pq=33$ on the IBM QASM simulator.}
+\end{figure*}
 
@@
 \bibitem{ibm} IBM, "Shor's algorithm",\\https://quantum-computing.ibm.com/docs/guide/q-algos/shor-s-algorithm
-\bibitem{github-repo} G. Muscarello, https://github.com/CapacitorSet/qiskit-fast-shor
+\bibitem{github-repo-main} G. Muscarello, https://github.com/CapacitorSet/shor-demonstration
+\bibitem{github-repo-shor} G. Muscarello, https://github.com/CapacitorSet/qiskit-fast-shor
 \end{thebibliography}
